What's hot and what's not:\\Windowed developer topic analysis

### 2009-07-01 lda-paper.tex
ack change
Thank yous
Final edits!

Software managers know that --- during any given development cycle ---
there is usually a difference between the set of tasks that developers
are supposed to be working on and the tasks they are actually working
on.  To better understand the realities of development, it would be
helpful to be able to answer questions such as: What topics dominated
the previous release cycle? Given the requirements agreed to at the
start of the iteration how much work did our developers spend on them?
What other tasks did they work on?  Which topics seem to recur over
and over between cycles?  How long do different topics persist?  Are
there latent cause-effect relationships between different topics?

@@

In terms of clustering and finding topic distributions, Latent
Dirichlet Allocation (LDA)~\cite{944937} competes with Latent Semantic
Indexing
%(LSI)~\cite{1421013,1374321,10.1109/ICPC.2007.13,10.1109/ICPC.2006.17},
(LSI)~\cite{1374321-short,10.1109/ICPC.2007.13-short},
probabilistic Latent Semantic Indexing (pLSI)~\cite{944937} and
semantic clustering~\cite{1698774-short,1566153-short}. These tools are used for
document modelling, document clustering and collaborative
filtering. LDA attempts to encode documents as a mixture
model, a combination of topics.  LDA has been used in software engineering
literature~\cite{lukins2008-short,10.1109/MSR.2007.20-short}%,NIPS2007637,1321709}.
to extract topics from documents such as methods, bug
reports, source code and files.

@@

In order to infer or associate the expertise of an author with topics
extracted from SCS, Linstead et al.\  proposed an author-source-code model
using LDA~\cite{10.1109/MSR.2007.20-short}.%,NIPS2007637,1321709}. 
This model associates authors and topics via their associated documents.

@@

Grant et al.~\cite{scottcordy} and have used an alternative technique,
called Independent Component Analysis~\cite{delac-short} to separate topic signals from
software code.

@@

Imagine that we are analyzing one month of development in a project
where there were three major tasks: bug fixing, adding a new GUI, and
documentation updates relating to the system and the GUI. To use LDA
we would get the word distributions of each commit messages, 
\begin{comment}
pass them to
LDA and tell LDA to find some topics, in this case we
in this case we chose to concentrate on four topics.
 The four
topics it discovered would ideally be bug fixing, GUI, documentation
and other. These topics are essentially word distributions, for
example the bug fixing topic would include words like \emph{bug},
\emph{fix}, \emph{failure} and \emph{ticket}. The GUI topic would
include words like \emph{widget}, \emph{panel}, \emph{window}, and
\emph{menu}. The documentation topic would include words like
\emph{section}, \emph{figure}, and \emph{chapter}. The other topic
would include words found in topics generally independent of the other
topics. If we analyzed a commit of a bug fix it would probably contain
words like \emph{ticket} and thus heavily associate with the bug fix
topic. A commit that was about user documentation regarding the GUI
would be associated with the documentation topic and the GUI topic
because it shared words from both topics. Where as a topic dealing
neither bugs, GUIs or documentation might be associated with the other
topic. This example demonstrates how LDA can associate one document (a
commit message) with more than one topic, and how topics are related to
documents via their word distributions. LDA also would discover these
independent topics in an unsupervised manner. All the end user has to
do is name the topic based upon the most frequent words in that topic,
which is a word distribution.
\end{comment}
% (please preserve the italics you put in ... I had to edit this in plain text so they got lost)
and have the LDA tool extract a set of topics from the data.  Ideally,
the LDA analysis would return four topics, corresponding to bug
fixing, GUI implementation, documentation, and ``other''.  Each topic
essentially corresponds to a word distribution.  For example, the bug
fixing topic might include words such as \emph{bug}, \emph{fix}, \emph{failure}, and
\emph{ticket}, while the GUI topic might include \emph{widget}, \emph{panel}, \emph{window}, and
\emph{menu}, and the documentation topic might include \emph{section}, \emph{figure}, and
\emph{chapter}.  The last topic would include words that were not commonly
found in bug reports, GUI fixing, or documentation commits; that is,
the LDA analysis would put into this last category the words that were
independent of the other topics it found.

@@

We found there were common words across topic clusters, such as
\emph{diffs}, \emph{annotate} and \emph{history}.
Words like these could be treated as stop words, since they occur
across many of the topics and since they relate to the mechanisms of
version control rather than the semantic content of the commit.
% since these words
%occur so often in the MySQL 3.23 messages. These words probably should
%be viewed as stop words since occur across so many topics, even though
%they are related to version control usage.  
There were topics which appeared only during some transitional period and never again
such as \emph{RENAME} and \emph{BitKeeper}. \emph{BitKeeper} which appears when MySQL switched to  BitKeeper for their SCS.
% There were notable
% transitional topics such as in the first window the word
% \emph{BitKeeper} appears because MySQL adopted Bitkeeper for their
% source control system yet in the following windows there were no
% mentions of BitKeeper. 
%\emph{RENAME} also only appeared once in the
%first window and never again.
For each topic we tried to find a word to describe its purpose.
To our surprise we found that even with only a
little familiarity with the code base that naming the topic was
straightforward. To find the purpose of a commit we looked at the most
frequent words in the word distribution of the topic and tried to
summarize the topic, then we looked into the commits related to that
topic to investigate if we were correct; since the commit messages and
the word distribution share the same words the purpose extracted from
top 10 words was usually accurate.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.9\textwidth]{commit-to-topics} 
  \caption{How commits are analyzed and aggregated into topics and trends: commits are first extracted, then abstracted into word counts or word distributions which are then given to topic analysis tool like LDA. LDA finds independent word distributions (topics) that these documents are related to (the numbers indicate similarity between documents and topics).}
  \label{fig:commits}
\end{figure*}

@@

%XXX maybe fix
The documents we are analyzing are the commit log comments, i.e., the
comments that are added when revisions to the project are committed.
% For each commit log comment, we count the occurrence of each word in
% the message, remove stop words, and then produce word distributions
% for each message.  These distributions are then normalized by the size
% of the message, each count was divided by the total number of
% tokens. After all messages are processed the distributions are
% extended to include all words from all of the distributions.
% For each commit log comment, we count the occurrence of each word in
% the message, remove stop words, and then produce word distributions
% for each message, which are normalized (divided by) by the size
% of the message.
% After all messages are processed the distributions are
% extended to include all words from all of the distributions.
% 
%
For each commit log comment we produce word distributions by counting
the occurrence of each word in the message, removing stop words and
then normalizing the distribution by the size of message, in tokens.
% (dividing word counts by the number of tokens).  
After
all messages are processed the distributions are extended to include
all words from all of the distributions.

@@

Our input for topic similarity is the top 10 most common words of each
topic.  Each topic is compared to each other topic in the system,
given a certain threshold of similarity, such as 8 out of
top 10 matching words.  10 words were chosen because often people care
about top 10 comparison and it allowed for some common words to exist
%but not cause topics to match so closely.  
yet not produce too many trends.
We then apply the
transitive closure on similar topics to our set of topic similarities;
this is similar to modelling topics as nodes and similarity as arcs,
then fill flooding along the similarity arcs until we have partitioned
the topics into clusters of similar topics. Figure \ref{fig:closure}
illustrates clustering of topics by topic similarity. These clusters
of topics are called \emph{trends}. 
Trends indicate that a topic has occurred over more than one period during development.

@@

\shrinkit
\SubSection{Visualization}
\shrinkit
%       1. [ ] need the visualizer
  Visualization is an integral part of our topics analysis which
  allows us to quickly explore the topics and trends of a project.
  Visualizing the results %is desirable as it 
  allows us to explore the
  data from different points of view to address different questions:
  How are the topics spread over time?  How many independent topics
  per period were there?  What were the repeating trends?  Did the
  trends dominate, or did local topics dominate?  How contiguous were
  the trends?  
  To address these questions we will describe and employ multiple visualizations.
%  Since we have a variety of questions to answer we suggest multiple
%  visualizations, which we now describe.

@@

We have devised several techniques for visualizing these topics and
trends.  For all of these techniques if we find trends that have
continuous segments, then we plot those segments as joined
horizontally across time. One technique is the \emph{compact-trend-view},
shown in Figure \ref{fig:topicsmear} and Figure \ref{fig:zoomedsmear},
that displays trends as they occur on the time-based x-axis
(placement along the y-axis is arbitrary).  Another technique is
the \emph{trend-time-line}, shown in Figure \ref{fig:trendtimeline}, where
each trend gets it own distinct y-value, while the x-axis is time;
these topics are then each plotted on their own line across time as
they occur. Our final technique is the \emph{trend-histogram}, shown in Figure
\ref{fig:histogram} where we plot each trend on its own line but stack
up the segments of the trend, much like a histogram. Each topic has its top 10 words 
listed in descending order of frequency from top to bottom, this text is embedded inside the topic's box, which at this resolution requires the reader to zoom in electronically.
A trend has all of its topic text embedded side by side within the same trend box.

@@

 The \emph{trend-histogram} (Figure \ref{fig:histogram}) attempts
  to show a count of how often a trend reoccurs and how many topics
  are related to a trend. It is meant to show the distribution of
  trends by their size in topics and time-span.  The
\emph{trend-histogram} superficially resembles the trend-time-line.
However, in this view the trends are plotted together by stacking to
the left of their row, thus time information is lost.  The trends are
ordered by the number of topics in the trend.  The trend-histogram
shows the count of instances of a trend and thus indicates which
trends occur the most. Due to the large number of topics
(approximately $N$ topics multiplied by $M$ periods), given the
allotted space, it is often best to crop off the trends with only one
topic ($1\%$ to $10\%$ of the total topics), otherwise the tail is
long. The \emph{trend-histogram} summarizes the distribution of
trends ordered by size.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend-time-line: Trends plotted per month of MaxDB 7.500. Time in months are plotted along the x-axis, each row on the y-axis is associated with a trend ranked by size in descending order}         
  \label{fig:trendtimeline}
\end{figure}

@@

When we examined PostgreSQL's history from 1996 to 2004, which includes
over $20,000$ commits. We did not find many trends with two or more
topics, using a similarity of $7/10$. $7/10$ was chosen because it
preserve independent topics but seemed to be a threshold
value where more serious trends started to appear.

@@

If we kept the stop words, we found that the large trend consisted
mostly of stop words and non-stop words such as \emph{patch},
\emph{fix}, \emph{update}.  By decreasing the similarity constraint to
$1/2$ the largest most common trend, which stretched across
the entire development, contained these same words (\emph{patch},
\emph{fix}, \emph{update}). The second largest trend mentions Dal
Zotto, while the third largest trend mentions the \texttt{[PATCHES]}
mailing-list and the names of some patch contributors.  Other repeating
topics refer to portability with Win32, Central Europe Time (CEST)
from email headers, issues with ALTER TABLE and CVS branch merging
(CVS does not record merges explicitly).

@@

The plots we produced of MaxDB 7.500 were unlike those of the other
systems, as there was a period where no development occurred and thus
there were no topics or trends whatsoever (see the gap in Figure
\ref{fig:topicsmear}). Using a topic similarity of $7/10$ we evaluated
MaxDB 7.500. MaxDB 7.500's first period was from June 2004 to January
2005, and its second period was from June 2005 to June 2006. There
were a total of $8 600$ commits analyzed.

@@

The query optimizer was a topic that recurred during MaxDB's
development. In our plots, topics that mention \emph{optimizer} occur
four times, yet in the global-trend-view (Figure
\ref{fig:statictopics}, explained in Section \ref{sec:compare}) it is not in any of the topics. A query
optimizer is an important component of an DBMS, but as we have shown
it does not appear as a topic on its own. We tried to remove words to
see if we could get an \emph{optimizer} topic. After removing stop
words and then two of the most common words, the global analysis
finally found a topic with optimizer in its top 10 words. Our
analysis shows that optimizer was important but it had been obscured
by the global topic analysis, which used the entire history of
messages, but would have been noticed using the more local topic
analysis such as our windowed topic analysis, which used a window of
messages.

@@

We presented several visualization techniques that focused on
different aspects of the data: temporality of trends, trend size, and
a compact-trend-view. The compact-trend-view shows more
information than the views that global analysis could show, and it
indicates how focused a period is by the total number of topics. As
well, it shows topics by similarity so one can track trends across
time.  Our trend-histogram highlights and measures the
size of trends while our trend-time-line view shows how a topic
reoccurs over time. These visualizations help us  understand the common topics that developers focus on during
development. If implemented interactively an user could easily zoom in
and query for a summary of a topic or trend.
In summary, our work on windowed topic analysis shows the potential
for automatically determining key topics and trends across software
development projects .

@@

We wish to extend this study by further exploring parameter
  choices and their effects in terms of window overlap size and number
 of topics.
%  We want to explore parameters more across multiple projects,
%   what motivates the need for more or less topics.  Parameters
%   include: window overlapping, window overlap size, window size,
%   number of topics, etc.  We want to investigate the effects of
%   overlapping windows on this analysis. Do they make the trends too
%   long? Do they highlight some trends unnecessarily or are they more
%   because they are time agnostic. 
Another avenue of future work is automatic topic labelling. Given a word
distribution we should be able to automatically select a word or term
that describes that distribution. Potential external sources of topic
names include software engineering taxonomies, ontologies and
standards.
\newline\noindent{\small\textbf{Acknowledgements:} Thanks to Tudor Girba and Neil Ernst.}
%for their valuable feedback.}
\shrinkit
\bibliographystyle{latex8}

\shrinkit
\bibliography{lda-paper}

>>>>

Software managers know that --- during any given development cycle ---
there is usually a difference between the set of tasks that developers
are supposed to be working on and the tasks they are actually working
on.  To better understand the realities of development, it would be
helpful to be able to answer questions such as: What topics dominated
the previous release cycle? Given the requirements agreed to at the
start of the iteration how much work did our developers spend on them?
What other tasks did they work on?  Which topics seem to recur over
and over between releases?  How long do different topics persist?  Are
there latent cause-effect relationships between different topics?

@@

In terms of clustering and finding topic distributions, Latent
Dirichlet Allocation (LDA)~\cite{944937} competes with Latent Semantic
Indexing
%(LSI)~\cite{1421013,1374321,10.1109/ICPC.2007.13,10.1109/ICPC.2006.17},
(LSI)~\cite{1374321-short,10.1109/ICPC.2007.13-short},
probabilistic Latent Semantic Indexing (pLSI)~\cite{944937} and
semantic clustering~\cite{1698774-short,1566153-short}. These tools are used for
document modelling, document clustering and collaborative
filtering. LDA attempts to encode documents as a mixture
model, a combination of topics.  LDA has been used in software engineering
literature~\cite{lukins2008-short,10.1109/MSR.2007.20-short} to %,NIPS2007637,1321709}.
extract topics from documents such as methods, bug
reports, source code and files.

@@

In order to infer or associate the expertise of an author with topics
extracted from SCS, Linstead et al.\  proposed an author-source-code model
using LDA~\cite{10.1109/MSR.2007.20-short}. This %,NIPS2007637,1321709}. 
model associates authors and topics via their associated documents.

@@

Grant et al.~\cite{scottcordy-short} and have used an alternative technique,
called Independent Component Analysis~\cite{delac-short} to separate topic signals from
software code.

@@

Imagine that we are analyzing one month of development in a project
where there were three major tasks: bug fixing, adding a new GUI, and
documentation updates relating to the system and the GUI. To use LDA
we would get the word distributions of each commit message, 
\begin{comment}
pass them to
LDA and tell LDA to find some topics, in this case we
in this case we chose to concentrate on four topics.
 The four
topics it discovered would ideally be bug fixing, GUI, documentation
and other. These topics are essentially word distributions, for
example the bug fixing topic would include words like \emph{bug},
\emph{fix}, \emph{failure} and \emph{ticket}. The GUI topic would
include words like \emph{widget}, \emph{panel}, \emph{window}, and
\emph{menu}. The documentation topic would include words like
\emph{section}, \emph{figure}, and \emph{chapter}. The other topic
would include words found in topics generally independent of the other
topics. If we analyzed a commit of a bug fix it would probably contain
words like \emph{ticket} and thus heavily associate with the bug fix
topic. A commit that was about user documentation regarding the GUI
would be associated with the documentation topic and the GUI topic
because it shared words from both topics. Where as a topic dealing
neither bugs, GUIs or documentation might be associated with the other
topic. This example demonstrates how LDA can associate one document (a
commit message) with more than one topic, and how topics are related to
documents via their word distributions. LDA also would discover these
independent topics in an unsupervised manner. All the end user has to
do is name the topic based upon the most frequent words in that topic,
which is a word distribution.
\end{comment}
% (please preserve the italics you put in ... I had to edit this in plain text so they got lost)
and have the LDA tool extract a set of topics from the data.  Ideally,
the LDA analysis would return four topics, corresponding to bug
fixing, GUI implementation, documentation, and ``other''.  Each topic
essentially corresponds to a word distribution.  For example, the bug
fixing topic might include words such as \emph{bug}, \emph{fix}, \emph{failure}, and
\emph{ticket}, while the GUI topic might include \emph{widget}, \emph{panel}, \emph{window}, and
\emph{menu}, and the documentation topic might include \emph{section}, \emph{figure}, and
\emph{chapter}.  The last topic would include words that were not commonly
found in bug reports, GUI fixing, or documentation commits; that is,
the LDA analysis would put into this last category the words that were
independent of the other topics it found.

@@

We found there were common words across topic clusters, such as
\emph{diffs}, \emph{annotate} and \emph{history}.
Words like these could be treated as stop words, since they occur
across many of the topics and since they relate to the mechanisms of
version control rather than the semantic content of the commit.
% since these words
%occur so often in the MySQL 3.23 messages. These words probably should
%be viewed as stop words since occur across so many topics, even though
%they are related to version control usage.  
There were topics which appeared only during some transitional period and never again,
such as \emph{RENAME} and \emph{BitKeeper}. \emph{BitKeeper} which appears when MySQL switched to  BitKeeper for their SCS.
% There were notable
% transitional topics such as in the first window the word
% \emph{BitKeeper} appears because MySQL adopted Bitkeeper for their
% source control system yet in the following windows there were no
% mentions of BitKeeper. 
%\emph{RENAME} also only appeared once in the
%first window and never again.
For each topic we tried to find a word to describe its purpose.
To our surprise we found that even with only a
little familiarity with the code base that naming the topic was
straightforward. To find the purpose of a commit we looked at the most
frequent words in the word distribution of the topic and tried to
summarize the topic, then we looked into the commits related to that
topic to investigate if we were correct; since the commit messages and
the word distribution share the same words the purpose extracted from
the top 10 words was usually accurate.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.9\textwidth]{commit-to-topics} 
  \caption{How commits are analyzed and aggregated into topics and trends: commits are first extracted, then abstracted into word counts or word distributions which are then given to a topic analysis tool like LDA. LDA finds independent word distributions (topics) that these documents are related to (the numbers indicate similarity between documents and topics).}
  \label{fig:commits}
\end{figure*}

@@

%XXX maybe fix
The documents we are analyzing are the commit log comments, i.e., the
comments that are added when revisions to the project are committed.
% For each commit log comment, we count the occurrence of each word in
% the message, remove stop words, and then produce word distributions
% for each message.  These distributions are then normalized by the size
% of the message, each count was divided by the total number of
% tokens. After all messages are processed the distributions are
% extended to include all words from all of the distributions.
% For each commit log comment, we count the occurrence of each word in
% the message, remove stop words, and then produce word distributions
% for each message, which are normalized (divided by) by the size
% of the message.
% After all messages are processed the distributions are
% extended to include all words from all of the distributions.
% 
%
For each commit log comment we produce word distributions by counting
the occurrence of each word in the message, removing stop words and
then normalizing the distribution by the size of the message, in tokens.
% (dividing word counts by the number of tokens).  
After
all messages are processed the distributions are extended to include
all words from all of the distributions.

@@

Our input for topic similarity is the top 10 most common words of each
topic.  Each topic is compared to each other topic in the system,
given a certain threshold of similarity, such as 8 out of
top 10 matching words.  10 words were chosen because often people care
about top 10 comparisons and it allowed for some common words to exist
%but not cause topics to match so closely.  
yet not produce too many trends.
We then apply the
transitive closure on similar topics to our set of topic similarities;
this is similar to modelling topics as nodes and similarity as arcs,
then fill flooding along the similarity arcs until we have partitioned
the topics into clusters of similar topics. Figure \ref{fig:closure}
illustrates clustering of topics by topic similarity. These clusters
of topics are called \emph{trends}. 
Trends indicate that a topic has occurred over more than one period during development.

@@

\shrinkit
\SubSection{Visualization}
\shrinkit
%       1. [ ] need the visualizer
  Visualization is an integral part of our topic analysis which
  allows us to quickly explore the topics and trends of a project.
  Visualizing the results %is desirable as it 
  allows us to explore the
  data from different points of view to address different questions:
  How are the topics spread over time?  How many independent topics
  per period were there?  What were the repeating trends?  Did the
  trends dominate, or did local topics dominate?  How contiguous were
  the trends?  
  To address these questions we will describe and employ multiple visualizations.
%  Since we have a variety of questions to answer we suggest multiple
%  visualizations, which we now describe.

@@

We have devised several techniques for visualizing these topics and
trends.  For all of these techniques if we find trends that have
continuous segments, then we plot those segments as joined
horizontally across time. One technique is the \emph{compact-trend-view},
shown in Figure \ref{fig:topicsmear} and Figure \ref{fig:zoomedsmear},
that displays trends as they occur on the time-based x-axis
(placement along the y-axis is arbitrary).  Another technique is
the \emph{trend-time-line}, shown in Figure \ref{fig:trendtimeline}, where
each trend gets its own distinct y-value, while the x-axis is time;
these topics are then each plotted on their own line across time as
they occur. Our final technique is the \emph{trend-histogram}, shown in Figure
\ref{fig:histogram} where we plot each trend on its own line but stack
up the segments of the trend, much like a histogram. Each topic has its top 10 words 
listed in descending order of frequency from top to bottom, this text is embedded inside the topic's box, which at this resolution requires the reader to zoom in electronically.
A trend has all of its topic text embedded side by side within the same trend box.

@@

 The \emph{trend-histogram} (Figure \ref{fig:histogram}) attempts
  to show a count of how often a trend reoccurs and how many topics
  are related to a trend. It is meant to show the distribution of
  trends by their size in topics and time-span.  The
\emph{trend-histogram} superficially resembles the trend-time-line.
However, in this view the trends are plotted together by stacking to
the left of their row, thus time information is lost.  The trends are
ordered by the number of topics in the trend.  The trend-histogram
shows the count of instances of a trend and thus indicates which
trends occur the most. Due to the large number of topics
(approximately $N$ topics multiplied by $M$ periods), given the
allotted space, it is often best to crop off the trends with only one
topic ($90\%$ to $99\%$ of the total topics), otherwise the tail is
long. The \emph{trend-histogram} summarizes the distribution of
trends ordered by size.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend-time-line: Trends plotted per month of MaxDB 7.500. Time in months are plotted along the x-axis, each row on the y-axis is associated with a trend ranked by size in descending order.}         
  \label{fig:trendtimeline}
\end{figure}

@@

We examined PostgreSQL's history from 1996 to 2004, which includes
over $20,000$ commits. We did not find many trends with two or more
topics, using a similarity of $7/10$. $7/10$ was chosen because it
preserve independent topics but seemed to be a threshold
value where more serious trends started to appear.

@@

If we kept the stop words, we found that the large trend consisted
mostly of stop words and non-stop words such as \emph{patch},
\emph{fix}, \emph{update}.  By decreasing the similarity constraint to
$1/2$, the largest most common trend, which stretched across
the entire development, contained these same words (\emph{patch},
\emph{fix}, \emph{update}). The second largest trend mentions Dal
Zotto, while the third largest trend mentions the \texttt{[PATCHES]}
mailing-list and the names of some patch contributors.  Other repeating
topics refer to portability with Win32, Central Europe Time (CEST)
from email headers, issues with ALTER TABLE, and CVS branch merging
(CVS does not record merges explicitly).

@@

The plots we produced of MaxDB 7.500 were unlike those of the other
systems, as there was a period where no development occurred and thus
there were no topics or trends whatsoever (see the gap in Figure
\ref{fig:topicsmear}). Using a topic similarity of $7/10$ we evaluated
MaxDB 7.500. MaxDB 7.500's first period was from June 2004 to January
2005, and its second period was from June 2005 to June 2006. There
were a total of $8,600$ commits analyzed.

@@

The query optimizer was a topic that recurred during MaxDB's
development. In our plots, topics that mention \emph{optimizer} occur
four times, yet in the global-trend-view (Figure
\ref{fig:statictopics}, explained in Section \ref{sec:compare}) it is not in any of the topics. A query
optimizer is an important component of a DBMS, but as we have shown
it does not appear as a topic on its own. We tried to remove words to
see if we could get an \emph{optimizer} topic. After removing stop
words and then two of the most common words, the global analysis
finally found a topic with optimizer in its top 10 words. Our
analysis shows that optimizer was important but it had been obscured
by the global topic analysis, which used the entire history of
messages, but would have been noticed using the more local topic
analysis such as our windowed topic analysis, which used a smaller window of
messages.

@@

We presented several visualization techniques that focused on
different aspects of the data: temporality of trends, trend size, and
a compact-trend-view. The compact-trend-view shows more
information than the views that global analysis could show, and it
indicates how focused a period is by the total number of topics. As
well, it shows topics by similarity so one can track trends across
time.  Our trend-histogram highlights and measures the
size of trends while our trend-time-line view shows how a topic
reoccurs over time. These visualizations help us  understand the common topics that developers focus on during
development. If implemented interactively, a user could easily zoom in
and query for a summary of a topic or trend.
In summary, our work on windowed topic analysis shows the potential
for automatically determining key topics and trends across software
development projects .

@@

We wish to extend this study by further exploring parameter
  choices and their effects in terms of window overlap size and number
 of topics.
%  We want to explore parameters more across multiple projects,
%   what motivates the need for more or less topics.  Parameters
%   include: window overlapping, window overlap size, window size,
%   number of topics, etc.  We want to investigate the effects of
%   overlapping windows on this analysis. Do they make the trends too
%   long? Do they highlight some trends unnecessarily or are they more
%   because they are time agnostic. 
Another avenue of future work is automatic topic labelling. Given a word
distribution we should be able to automatically select a word or term
that describes that distribution. Potential external sources of topic
names include software engineering taxonomies, ontologies and
standards.
%\newline\noindent{\small\textbf{Acknowledgements:} We'd like to thank Tudor Girba and Neil Ernst.}
%\newline\noindent{\small\textbf{Acknowledgements:} We thank Tudor Girba for his comments.}
\newline\noindent{\small\textbf{Acknowledgements:} We would like to thank Tudor Girba and Neil Ernst for their feedback and ideas.}
%\newline\noindent{\small\textbf{Acknowledgements:} We thank Tudor Girba and Neil Ernst.}
%We'd like to thank Tudor Girba and Neil Ernst.}
%for their valuable feedback.}
\shrinkit
\bibliographystyle{latex8}
\shrinkit
\shrinkit
\bibliography{lda-paper}
